### 2017-06-26 report/report.tex
update

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\linespread{1.1}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage[nottoc]{tocbibind}
\usepackage{listings}
\setcounter{secnumdepth}{4}
\usepackage{tikz}
\usepackage{xfrac}
\usetikzlibrary{arrows.meta}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily}
}
\begin{document}

@@

\section{Introduction}
"In order to generate relevant recommendations, a context-aware recommender system (CARS) not only makes use of user preferences, but also exploits information about the specific contextual situation in which the recommended item will be consumed." \cite{Baltrunas:2012:CRA:2339097.2339111}

This is in contrast with the fact that most of the available music recommender systems suggest music without taking into consideration the user context \cite{Knees:2013:SMS:2559928.2542206}. This is because defining and especially exploiting contexts is not a trivial operation. Context can be defined as any information that can be used to characterize the situation of an entity. \cite{Dey:2001:UUC:593570.593572}. These informations informations includes mood, location, activity, friends, daily and current activities of the target user.

If we think of a recommender task in a mobile scenario (e.g., choosing a song while sightseeing), we see that most recommendations are requested by users while they are on their way. This causes a continuous change in the context that needs to be carefully addressed. Recommendations are much more useful and enjoyable for end users as they change with their current context . \cite{Ostuni:2012:CCM:2887638.2887642}

@@

\subsection{Motivation and context}
In the past, many tried to link POIs and music in many different ways. Someone managed to link music and POIs by using a common set of tags that describe emotional properties both for music and POIs \cite{Kaminskas:2013:LMR:2507157.2507180}. This method is completely supervised, in fact it requires the definition of a set of emotions for songs and POIs. This operation must be done manually and is hardly scalable.
\begin{figure}[!htb]
  \centering 
    \includegraphics[width=1\textwidth]{images/semantic_net.png}
    \caption{Semantic Network with predefined classes}
\end{figure}

In a second project \cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia \footnote{DBpedia: http://wiki.dbpedia.org/} to a set classes related to the domains of interest. These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic informations. In this way, they managed to find relations in a set of paths constrained to pass through those classes.

Looking at the future propositions, both projects proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
In order to do this, they proposed to use Relfinder \cite{Heim:2009:RRR:1695324.1695351} and set the connection weights using an heuristic. In fact, one of the disadvantages of those approaches is that connections weights are assigned by experts and were not provided in the paper.
Our intention is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a pathfinder that finds paths and a path discriminator that selects the interesting relations. We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities. Moreover, we will use different datasets with the intention to exploit their implicit advantages and obtain overall a better recommender system.

@@

\subsection{Contributions}
In this project, we show a new approach for finding artists linked to a place of interest (POI). We propose an entity linking framework built upon DBpedia, 3cixty \footnote{3cixty: https://www.3cixty.com/}, and Doremus \footnote{DOREMUS: http://www.doremus.org/} that is able to reach editorial accuracy in the interlinking process. Furthermore, we present a graph exploration algorithm that is able to find deep connections in a short time and discriminate between them by looking at those that can be the most interesting.

\subsection{Report structure}
The report is divided into five sections, one for each part of the project. The first two parts are about linking external datasets to DBpedia, this is also known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
The third treats the Pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
The fourth describes the whole implementation of the REST API that allows the application to work smoothly.
The fifth part covers the mobile web application and the technologies involved in its functioning.

\section{Interlinking and enriching POIs}
\subsection{Problem description}
Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking have been proposed, but this is still an active research topic.
One of the main problems that must be faced in an interlinking process is the ontology definition, in fact, specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it. This means that in the case of POIs, not all places in nice are linked to nice, thus it is difficult to even correctly define a POI in Nice.
Since we are dealing with a medium sized city such as Nice, we can't allow loosing some matchings and we need to carefully analyze the DBpedia ontology in order to leave out a minimum part of Nice POIs.

\subsection{Datasets: 3cixty, DBpedia, Wikidata}
\subsubsection{3cixty}
3cixty is a semantic dataset that contains aggregated informations of POIs and events. The dataset is the result of an aggregation process that join the POI informations from different datasets e.g. Facebook, Foursquare, Yelp \dots
In this project 3cixty is used as a trusted source of POIs for Nice.
POIs have many informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint selecting the Nice city.
\subsubsection{DBpedia}
DBpedia is a project that aims at connecting the semantic world. We used it to get the POIs in Nice.
In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint. POIs are retrieved using two different sparql queries that target different kind of resources:
\begin{enumerate}
\item We perform a query that looks for all Geoentities that are in the area of nice. An entity is in the area of Nice if its coordinates are in a custom box that contains all the area of Nice.
Unfortunately there are many POIs that are without coordinates,so they are not selected by this query.
\begin{lstlisting}
SELECT ?place ?placeLabel ?lat ?long
WHERE {
    ?place geo:lat ?lat.
    ?place geo:long ?long.
    ?place rdfs:label ?placeLabel.
    FILTER(
      xsd:double(?lat)  <= 43.80 &&
      xsd:double(?lat) >= 43.63 &&
      xsd:double(?long) <= 7.36 &&
      xsd:double(?long) >= 7.14
    )
}
\end{lstlisting}
\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/Nice.png}
    \caption{Area for POIs selection}
\end{figure}

\item We take all resources that have as a parent either the Nice resource or the Category:Nice resource. Then we repeat this operation for each subcategory of Category:Nice in a recursive way. Among these resources, we keep those which type is in a set of classes defined by hand.
\end{enumerate}
\subsubsection{Wikidata}
Wikidata \footnote{Wikidata: https://www.wikidata.org/} is a project that aims at connecting the semantic world. We used it to get the POIs in Nice. Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced. This means that it is easier to select what we want. Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query. Since wikidata supports complex geo-based queries, we can make a query that looks for all POIs in a range of 25 Kilometers from the center of Nice.
\subsection{Entity Linking process}
In order to link our two set, we copy them locally and then we perform the linking process. Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries.
\subsubsection{Properties}
The first phase is to actually get the interesting properties of the entities. Regarding those that come from DBpedia, we use only the labels. Regarding the labels, we take them in all the available languages. In this way we can do a multilingual match that improves our accuracy. Since this is not intuitive, here is an example.
DBpedia labels:
'Conservatory of Nice'
'Conservatoire de Nice'
3cixty label: 'Conservatoire de nice'
In this case if we use the english label, we do not obtain a perfect match, while with the french label we obtain a perfect match.
We do not use coordinates because not all entities have them. Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because they are inaccurate.
Regarding 3cixty entities, they have very accurate coordinates, and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.

\subsubsection{Transformations}
At this point of the pipeline, we have labels that are encoded into unicode utf-8. Common similarity metrics accepts only plain ASCII strings as input, so we need to convert them into ASCII. Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels. This is done in an intelligent way using the python library \textit{'unidecode'}\footnote{Unidecode: https://pypi.python.org/pypi/Unidecode}, that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters. For example, an accented letter like 'è' can't be represented in ASCII, and most of the libraries simply delete it, while \textit{'unidecode'} converts it to the nearest ASCII character: in this case 'è' is converted to 'e'. In this way we can retain most of the original information after this conversion process.

The second step is probably the most important, and is the normalization of names. Some similarity metrics are extremely sensitive to noise. For example, when we use simple levenstein distance between ('airport','airport nice') is 5, while the distance ('airport','port') is 4. This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one. In order to fix this problem we add the city name to all the labels where it is not present.

The third step is to strip all non alphabetical characters and to convert to lowercase all strings, this off course gives us cleaner strings to compare.
The whole transformation pipeline aims at maximizing the similarity measure between correct matches. This is extremely important, because later we can set a threshold to separate matches that have a good confidence from matches with a low confidence. If we do not perform the transformation phase, we would obtain correct matches that have the same confidence of the incorrect ones because we have basically some noise in all the strings.

\subsubsection{Similarity measures and matching algorithm}
Now that strings are clean, we can proceed to the actual matching. A first problem rises: we want to match a 3cixty poi to a dbpedia poi, or we want to match a dbpedia poi to a 3cixty poi? In the first case we are sure that each 3cixty poi will be matched to a single dbpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi. Alternatively, we are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that many DBpedia poi are matched to the same 3cixty poi.
Regarding DBpedia, we are sure that POIs are univoque, while we know that for the same POI, in 3cixty there are multiple ones.
Since at the end we will be using 3cixty coordinates, we opt for the first choice: if a DBpedia poi will be matched to multiple 3cixty pois, than we will follow an heuristic to choose the best match.

Regarding the similarity metric among strings, we use multiple similarity measures based on levenstein distance. We chose to use different metrics because we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough. From a technical point of view, we used a set of the similarity metrics provided by the 'fuzzywuzzy'\footnote{FuzzyWuzzy: https://pypi.python.org/pypi/fuzzywuzzy} python module.

\subsubsection{Aggregations}
Until now, we took one by one the 3cixty labels and we calculated the different similarity metrics against all DBpedia labels. 
The aggregation algorithm is run for each 3cixty POI and can be described as follow:
\begin{enumerate}
\item For each similarity metric, take the three best matching labels and for each of them, calculate the average of all the similarity metrics.
\item The final match is the POI corresponding with the label with the highest score.
\end{enumerate}
Why we don't simply take the average, or the minimum, or the maximum?
The reasoning behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics. If a string is mediocre in all comparisons, then we do not trust it. Instead, with our methodology we are keeping only those matches that excel in some similarity metric, and then we take the one that performs better on average. We think that in this way we can filter out all those matches with average strings that matches almost anything.

\subsubsection{Filtering}
Now that the matching is done, we need to filter our results.

The first operation to do is to eliminate all those POIs that match with Nice, but that have a label different from Nice. This happens because we added Nice to all the strings. That addition was helpful, and it also created a safe default that we can easily filter.
Most of these POIs filtered in this way are acronyms that match with Nice e.g. 'ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.

The second operation to perform is the filtering based on the average score.
The average score can be interpreted as a confidence. Intuitively, high scores corresponds to correct matches, while low scores corresponds to bad matches.
The importance of the selection, transformation, similarity metric and aggregation pipeline is extremely high, in fact we want a confidence which we can trust. An untrusted confidence gives us no additional informations about good matches and bad matches.
At this point we filter all matches with a score below a given threshold.

Now we are at the half of our work, for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI. We aim to a 1 to 1 relation, so we need to choose among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
We have few possibilities:
\begin{enumerate}
\item Pick the POI that minimize the distance to all the other POIs, this is like applying the K-medoids clustering with K equal 1.
\item Pick the POI which is nearest to the center
\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available
\item Pick the POI which is nearest to the position found on Google Maps \footnote{Google Maps: https://www.google.fr/maps}
\item Link our data to GeoNames \footnote{GeoNames: http://www.geonames.org/}, a dataset of POIs
\end{enumerate}
The first method might be the best one, but it works if most of the POIs are actually clustered. If they are very sparse it does not work.
The second method is biased towards POIs near the center.
The third method can work only with DBpedia POIs with coordinates, and gives good results if DBpedia coordinates are good, but we already know that this is not true.
The fourth method might be the best one, but we need to look outside the semantic world and trust the Google Maps API. Here the problem is that we have no control over the API, but we  know that Google Maps is very good at matching a name with a place.
The fourth method could be the best one, in fact we can exploit GeoNames coordinates that are trusted. The main problem is the fact that not all DBpedia POIs have a corresponding POI.
For simplicity and reliability, we used the Google Maps API because we trust it.
We use the API by sending the DBpedia label to the service, the response contains the coordinates of the POI associated to the DBpedia label. At this point we select the nearest 3cixty POI and we keep it if the distance is less than 2 kilometers.
\subsection{Evaluation (Google Maps)}
The evaluation part is done using the Google Maps API. As done before, we use the distance between the 3cixty POI coordinates and the POI coordinates provided by the API. Since we used the Google Maps API during our process, we expect that distances are low, in fact we know that each POI distance is less than 2 kilometers. What we want to check here is the distance distribution.

\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/distance.png}
    \caption{distance distribution of POIs}
\end{figure}

Looking at the distance distribution we note that most of the POIs are actually near to the Google Maps coordinates, while for few POIs this is not true. The main reason for this is the inherent error that arise when we define a POI which occupies a big surface with coordinates that refer to a specific point. For example the surface of the airport of Nice is quite big and different services can locate it in different points of his surface. In the case of the airport, the distance is actually 500 meters. This means that if it is true that most of the POIs are under 500 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
At the end of our POI linking process we have 58 POIs that will be matched with the artists.

\section{Interlinking and enriching Artists}
\subsection{Problem description}
DBpedia contains Artists and their works in a disorganized way.
This consist a huge limit because we do not trust the data that we have in DBpedia. Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia. In order to have some order, we use DOREMUS, which contains trusted informations about artists and songs in a strict ontology.

\subsection{Datasets: DOREMUS, DBpedia, Wikidata}
\subsubsection{DOREMUS}
DOREMUS is a semantic dataset that aims to a fine description of musical works in the fields of traditional and classical music: related musical or creation events, relations to authors, cultural background, interpretations, social functions, etc.
With DOREMUS we can have absolute trust in the data regarding artists, and we can then found corresponding artists in DBpedia with a custom linking process.
Retrieving all artists from DOREMUS is extremely easy, in fact we just need to ask for the Persons in the datasets that are linked to a work at least. The performed query is written below; we retrieved not only the artist uri but also the artist name, the id,  the born year, the death year and the DBpedia "sameAs" already present. These informations are useful as input data for our similarity metric and for the final evaluation.

\begin{lstlisting}
select $uri_doremus 
(group_concat( distinct $id_doremus;separator="|||") as $id_doremus)
(group_concat(distinct $name_doremus;separator="|||") as $name_doremus) 
(group_concat(distinct $born_year;separator="|||") as $born_year) 
(group_concat( distinct $death_year;separator="|||") as $death_year) 
(group_concat(distinct $dbpedia;separator="|||") as $dbpedia) 
where {
$uri_doremus foaf:name $name_doremus.
$uri_doremus ecrm:P131_is_identified_by $id_doremus.
$uri_doremus a ecrm:E21_Person.
$activity ecrm:P14_carried_out_by $uri_doremus.
OPTIONAL{$uri_doremus owl:sameAs $dbpedia.
FILTER (strStarts(str($dbpedia), 'http://dbpedia.org/resource/'))}
OPTIONAL{$uri_doremus ecrm:P98i_was_born $born_year}
OPTIONAL{$uri_doremus ecrm:P100i_died_in $death_year}
} 
group by $uri_doremus
order by $name_doremus
\end{lstlisting}

>>>>

\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\linespread{1.1}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{textcomp}
\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
\usepackage[nottoc]{tocbibind}

\usepackage{listings}
\lstset{breaklines}
\setcounter{secnumdepth}{4}
\usepackage{tikz}
\usepackage{xfrac}
\usetikzlibrary{arrows.meta}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily}
}
\begin{document}

@@

\section{Introduction}
"In order to generate relevant recommendations, a context-aware recommender system (CARS) not only makes use of user preferences, but also exploits information about the specific contextual situation in which the recommended item will be consumed."~\cite{Baltrunas:2012:CRA:2339097.2339111}

This is in contrast with the fact that most of the available music recommender systems suggest music without taking into consideration the user context~\cite{Knees:2013:SMS:2559928.2542206}. This is because defining and especially exploiting contexts is not a trivial operation. Context can be defined as any information that can be used to characterize the situation of an entity~\cite{Dey:2001:UUC:593570.593572}. These informations informations includes mood, location, activity, friends, daily and current activities of the target user.

If we think of a recommender task in a mobile scenario (e.g., choosing a song while sightseeing), we see that most recommendations are requested by users while they are on their way. This causes a continuous change in the context that needs to be carefully addressed. Recommendations are much more useful and enjoyable for end users as they change with their current context~\cite{Ostuni:2012:CCM:2887638.2887642}.

@@

\subsection{Motivation and context}
In the past, different attempts have been performed to link POIs and music in many different ways. A strategy can consist in linking music and POIs by using a common set of tags that describe emotional properties both for music and POIs~\cite{Kaminskas:2013:LMR:2507157.2507180}. This method is completely supervised, in fact it requires the definition of a set of emotions for songs and POIs. This operation must be done manually and is hardly scalable.
\begin{figure}[!htb]
  \centering 
    \includegraphics[width=1\textwidth]{images/semantic_net.png}
    \caption{Semantic Network with predefined classes}
\end{figure}

In~\cite{Kaminskas:2012:KMR:2390848.2390854}, the goal is achieved by by restricting the subspace of DBpedia to a set classes related to the domains of interest. These classes includes concepts that are easily linkable to artists and POIs, such as historic periods, architectural styles and geographic informations. In this way, it is possible to find relations in a set of paths constrained to pass through those classes.
Looking at the future propositions, both strategies proposed the idea to exploit arbitrary semantic relations between POIs and musicians.
In order to do this, tools like Relfinder have been proposed \cite{Heim:2009:RRR:1695324.1695351}, in combination an heuristic to set the connection weights. In fact, one of the disadvantages of those approaches is that connections weights are assigned by experts and are not published.
Our goal is to build our approach on top of this paper and find relations in a completely unsupervised way: this means that we intend to define a path finder that finds paths and a path discriminator that selects the interesting relations.

@@

\subsection{Contributions}
In this project, we show a new approach for finding artists linked to a place of interest (POI). We propose an entity linking framework built upon DBpedia, 3cixty\footnote{3cixty: https://www.3cixty.com/}, and DOREMUS\footnote{DOREMUS: http://www.doremus.org/} that is able to reach editorial accuracy in the interlinking process. Furthermore, we present a graph exploration algorithm that is able to find deep connections in a short time and discriminate between them by looking at those that can be the most interesting.
We aim at reducing the need for human intervention in defining classes and weights with the hope that this approach will be completely data driven and easily scalable to different cities. 
Finally, we demonstrate the effectiveness of our work through an APP that  ....

For this experimental work, we chose Nice because because it is a medium sized city that allows us to deal with both popular and unpopular places. Furthermore the number of POIs in Nice is manageable, this means that we can check immediately our results. Finally, POIs in Nice are enough to see if our proposed solution can scale.

\subsection{Report structure}
This report is divided into five sections, one for each part of the project. The first two parts are about linking external datasets to DBpedia, this task is known as entity linking and we perform it in the optic of enriching our data with the inter-concept links present in DBpedia.
The third covers the Pathfinder, a module of our system that is able to find deep connections between two entities in DBpedia.
The fourth describes the whole implementation of the REST API that allows the application to work smoothly.
The fifth part covers the mobile web application and the technologies involved in its functioning.

\section{Interlinking and enriching POIs}
\subsection{Problem description}
Interlinking different datasets is not trivial, many approaches that aimed at a semi-supervised interlinking have been proposed, but this is still an active research topic.
One of the main problems that must be faced in an interlinking process is the ontology definition. In fact, specialized datasets tend to have a very strict ontology, while DBpedia does not enforce it. This means that in the case of POIs, not all places in Nice are linked to Nice, thus it is difficult to even correctly define a POI in Nice.
Since we are dealing with a medium sized city such as Nice, we can't allow loosing some matchings and we need to carefully analyze the DBpedia ontology in order to leave out the minimum part of Nice POIs.

\subsection{Datasets: 3cixty, DBpedia, Wikidata}
\subsubsection{3cixty}
3cixty is a semantic dataset that contains aggregated informations of POIs and events. The dataset is the result of an aggregation process that join the POI informations from different datasets e.g. Facebook, Foursquare, Yelp \dots
In this project 3cixty is used as a trusted source of POIs for Nice.
POIs have a lot of informations, such as the category, the address, comments from users, and coordinates. In order to get all the POIs in Nice, we simply used the POIs endpoint of the 3cixty API.

For example, this is the JSON object associated to the `Nice Lawn Tennis Club': \begin{lstlisting}
{  
   "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad",
   "businessType":[  
      "http://data.linkedevents.org/kos/foursquare/tennis-court"
   ],
   "geoLocation":{  
      "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad/geometry",
      "lat":43.7043,
      "long":7.25188
   },
   "label":"Nice Lawn Tennis Club",
   "location":{  
      "_about":"http://data.linkedevents.org/location/579aa423-cb1b-3d35-90d5-ef482aa093ad/address",
      "streetAddress":"5, ave. Suzanne Lenglen, 06000 Nice, France"
   }
}

\end{lstlisting}

\subsubsection{DBpedia}
DBpedia\footnote{DBpedia: http://wiki.dbpedia.org/} is a crowd-sourced community effort to extract structured information from Wikipedia\footnote{Wikidata: https://en.wikipedia.org/} and make this information available on the Web. The DBpedia knowledge base has several advantages over existing knowledge bases: it covers many domains; it automatically evolves as Wikipedia changes, and it is truly multilingual. 
We used it to get the POIs in Nice.
In order to get the POIs from DBpedia, it is necessary to perform SPARQL queries against the SPARQL endpoint. POIs are retrieved using two different SPARQL queries that target different kind of resources:
\begin{enumerate}
\item We perform a query that looks for all resources in Nice. 
Figure \ref{fig:box} shows the area with valid coordinates.
Unfortunately there are many POIs that are without coordinates, so they are not selected by this query.
\begin{lstlisting}
SELECT ?place ?placeLabel ?lat ?long
WHERE {
    ?place geo:lat ?lat.
    ?place geo:long ?long.
    ?place rdfs:label ?placeLabel.
    FILTER(
      xsd:double(?lat)  <= 43.80 &&
      xsd:double(?lat) >= 43.63 &&
      xsd:double(?long) <= 7.36 &&
      xsd:double(?long) >= 7.14
    )
}
\end{lstlisting}
\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/Nice.png}
    \caption{Area for POIs selection}
    \label{fig:box}
\end{figure}

\item We take all resources that have as a parent either the dbr:Nice resource or the dbc:Nice resource. Then we repeat this operation for each subcategory of dbc:Nice in a recursive way. Among these resources, we keep those which type is in a set of classes defined by hand.
\end{enumerate}
\subsubsection{Wikidata}
Wikidata\footnote{Wikidata: https://www.wikidata.org/} Wikidata is a free and open knowledge base that can be read and edited by both humans and machines. Wikidata acts as central storage for the structured data of its Wikimedia\footnote{Wikimedia: https://www.wikimedia.org/} sister projects including Wikipedia.

We used it to get the POIs in Nice. Respect to DBpedia, Wikidata has a well defined ontology that is strictly enforced. This means that it is easier to select what we want. Moreover, most of POIs in wikidata have coordinates, so we can get them with a single query. Since wikidata supports complex geo-based queries, we can make a query that looks for all POIs in a range of 25 Kilometers from the center of Nice.
\begin{lstlisting}
SELECT ?item ?itemLabel ?location WHERE {
  wd:Q33959 wdt:P625 ?niceLoc .
  SERVICE wikibase:label {
    bd:serviceParam wikibase:language "fr" .
  }.
  SERVICE wikibase:around { 
      ?item wdt:P625 ?location . 
      bd:serviceParam wikibase:center ?niceLoc . 
      bd:serviceParam wikibase:radius "10" . 
  }  
}
\end{lstlisting}

\subsection{Entity Linking process}
In order to link our three set, we copy them locally and then we perform the linking process. Having the entities locally is crucial, in fact it allows us to make way more complex operations respect to those that can be done with SPARQL queries. The whole process can be described as follow:
\begin{enumerate}
\item Extract labels from DBpedia entities.
\item Apply transformations.
\item Compute similarity metrics with 3cixty entities.
\item Aggregate results
\item Filter matches above threshold.
\end{enumerate}

\subsubsection{Properties}
The first phase is to actually get the interesting properties of the entities. Regarding those that come from DBpedia, we use only the labels. Regarding the labels, we take them in all the available languages. In this way we can do a multilingual match that improves our accuracy. 
Here is an example:
\begin{itemize}
\item DBpedia labels: `Conservatory of Nice' @en, `Conservatoire de Nice' @fr
\item 3cixty label: `Conservatoire de nice'
\end{itemize}
In this case if we use the English label, we do not obtain a perfect match, while with the French label we obtain a perfect match. Other times we have the opposite result, but using labels in different languages we solve this problem.

Among other informations, we have the coordinates, but we do not use them because not all entities have them. Moreover, we have seen experimentally that using the DBpedia coordinates we obtain worse results because of their inaccuracy.
Regarding 3cixty entities, they have very accurate coordinates and few labels. For this phase we do not need the coordinates, while regarding the labels, we keep the first one.

\subsubsection{Transformations}
At this point of the pipeline, we have labels that are encoded into unicode utf-8. Common similarity metrics accepts only plain ASCII strings as input, so we need to convert them into ASCII. Since utf-8 can represent way more characters than ASCII, we need to strip non ASCII characters from our labels. This is done in an intelligent way using the python library \textit{`unidecode'}\footnote{Unidecode: https://pypi.python.org/pypi/Unidecode}, that is able to convert from unicode to ASCII by changing or deleting a minimum set of characters. For example, an accented letter like `è' can't be represented in ASCII, and most of the libraries simply delete it, while \textit{`unidecode'} converts it to the nearest ASCII character: in this case 'è' is converted to 'e'. In this way we can retain most of the original information after this conversion process.

The second step is probably the most important, and is the normalization of names. Some similarity metrics are extremely sensitive to noise. For example, when we use simple Levenshtein:
\begin{itemize}
\item levenshtein\_distance(`airport',`airport nice'): 5
\item levenshtein\_distance(`airport',`port'): 4
\end{itemize}
This is enough to raise some concerns: the simple addition of the city name can turn a perfect match into a mediocre one. In order to fix this problem we add the city name to all the labels where it is not present.

The third step is to strip all non alphabetical characters and to convert to lowercase all strings, this off course gives us cleaner strings to compare.

The whole transformation pipeline aims at maximizing the similarity measure between correct matches. Later we will set a threshold to separate matches that have a good confidence from matches with a low confidence.

\subsubsection{Similarity measures and matching algorithm}
Now that strings are clean, we can continue to the actual matching. A first question rises: we want to match a 3cixty poi to a DBpedia poi, or we want to match a DBpedia poi to a 3cixty poi? In the first case we are sure that each 3cixty poi will be matched to a single DBpedia poi, but there is the risk that multiple 3cixty poi are matched to the same DBpedia poi. Alternatively, we are sure that each DBpedia poi is matched to at most a 3cixty poi, but there is the risk that many DBpedia poi are matched to the same 3cixty poi.
Regarding DBpedia, we are sure that POIs are univoque, while we know that for the same POI, in 3cixty there are multiple ones.
Since at the end we will be using 3cixty coordinates, we opt for the first choice: if a DBpedia poi will be matched to multiple 3cixty pois, than we will follow an heuristic to choose the best match.

Regarding the similarity metric among strings, we use multiple similarity measures based on Levenshtein distance. This comes from the fact that experimentally we have seen experimentally that in this specific case, strings that represents POIs, a single similarity metric is not enough. From a technical point of view, we used a set of the similarity metrics provided by the `fuzzywuzzy'\footnote{FuzzyWuzzy: https://pypi.python.org/pypi/fuzzywuzzy} python module:
\begin{itemize}
\item partial\_ratio: Return the ratio of the most similar substring
    as a number between 0 and 100.
\item token\_set\_ratio: Find all alphanumeric tokens in each string:
\begin{enumerate}
\item treat them as a set
\item construct two strings of the form: $<sorted\_intersection> <sorted\_remainder>$
\item take ratios of those two strings
\item controls for unordered partial matches
\end{enumerate}

\item token\_sort\_ratio: Return a measure of the sequences' similarity between 0 and 100
    but sorting the token before comparing.
\item partial\_token\_sort\_ratio: Return the ratio of the most similar substring as a number between 0 and 100 but sorting the token before comparing.

\item WRatio: A weighted combination of other similarities
\end{itemize}

\subsubsection{Aggregations}
Until now, we took one by one the 3cixty labels and we calculated the different similarity metrics against all DBpedia labels. 
The aggregation algorithm is run for each 3cixty POI and can be described as follow:
\begin{enumerate}
\item For each similarity metric, take the three best matching labels and for each of them, calculate the average of all the similarity metrics.
\item The final match is the POI corresponding with the label with the highest score.
\end{enumerate}
Why we don't simply take the average, or the minimum, or the maximum?
The reason behind this is that by taking the average we are flattening all the scores, and there is the risk that the string with the highest similarity is a string that is mediocre in all the different metrics. If a string is mediocre in all comparisons, then we do not trust it. Instead, with our methodology we are keeping only those matches that excel in some similarity metric, and then we take the one that performs better on average. In this way we can filter out all those matches with average strings that matches almost anything.

\subsubsection{Filtering}
Now that the matching is done, we need to filter our results.
The first operation to do is to ignore all those POIs that match with Nice, but that have a label different from Nice. This happens because we added Nice to all the strings. That addition was helpful, and it also created a safe default that we can easily filter.
Most of the POIs filtered in this way are acronyms that match with Nice, e.g. `ATP Nice' matches with Nice because half of the string is Nice and is artificial, because we added it.

The second operation to perform is the filtering based on the average score.
The average score can be interpreted as a confidence. Intuitively, high scores corresponds to correct matches, while low scores corresponds to bad matches.
The importance of the selection, transformation, similarity metric and aggregation pipeline is extremely high, in fact we want a confidence which we can trust. An untrusted confidence gives us no additional informations about good matches and bad matches.
At this point we filter all matches with a score below a given threshold(0.8).

In this moment for each 3cixty POI we have a link to a DBpedia POI, but we might have multiple 3cixty POIs linked to the same DBpedia POI. We aim to a 1 to 1 relation, so we need to choose one among a group of 3cixty POIs linked to the same DBpedia POI, the most representative.
We have few possibilities:
\begin{enumerate}
\item Pick the POI that minimize the distance to all the other POIs, this is like applying the K-medoids clustering with K equal 1. This works if POIs are actually clustered, while it does not work if they are sparse.
\item Pick the POI which is nearest to the center. This is biased towards POIs near the center.
\item Pick the POI which is nearest to the DBpedia POI, if coordinates are available. This works only with a subset of POIs, and we do not fully rely on DBpedia coordinates.
\item Pick the POI which is nearest to the position found on Google Maps\footnote{Google Maps: https://www.google.fr/maps}. We have no control over Google Maps.
\item Link our data to GeoNames\footnote{GeoNames: http://www.geonames.org/}. Not all DBpedia POIs have a corresponding GeoNames POI.
\end{enumerate}
For simplicity and reliability, we used the Google Maps API because we trust it.
We use the API by sending the DBpedia label to the service, the response contains the coordinates of the POI associated to the DBpedia label. At this point we select the nearest 3cixty POI and we keep it if the distance is less than 2 kilometers.
\subsection{Evaluation (Google Maps)}
The evaluation part is done using the Google Maps API. As done before, we use the distance between the 3cixty POI coordinates and the POI coordinates provided by the API. Since we used the Google Maps API during our process, we expect that distances are low, in fact we know that each POI distance is less than 2 kilometers. What we want to check here is the distance distribution.

\begin{figure}[!htb]
  \centering 
    \includegraphics[width=0.5\textwidth]{images/distance.png}
    \caption{distance distribution of POIs}
    \label{fig:poidist}
\end{figure}

Figure \ref{fig:box} shows the POIs distance distribution with the corresponding Google Maps POIs. If we consider 250 meters as a threshold, 70\% of POIs are below it. The main reason for this is the inherent error that arise when we define a POI which occupies a big surface with coordinates that refer to a specific point. For example the surface of the airport of Nice is quite big and different services can locate it in different points of his surface. In the case of the airport, the distance is actually 500 meters. This means that if it is true that most of the POIs are under 250 meters, we can't use this as a threshold because we would leave out a large part of the correct POIs.
At the end of our POI linking process we have 58 POIs.

\section{Interlinking and enriching Artists}
\subsection{Problem description}
DBpedia Artists and Works are not represented with a strict ontology. 
This is a huge limit because we can not rely entirely on the data that we have in DBpedia. Even the simpler operations, such as finding all artists and all songs are extremely difficult due to the non-strict ontology of DBpedia. In order to have some order, we use DOREMUS, which contains trusted and properly organized informations about artists and songs.
